\documentclass{IEEEtran}

\usepackage{graphicx}
\usepackage{setspace}
\usepackage{flushend}
\usepackage{color}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hhline}
\usepackage{oz}


   \linespread{2}
%\makeatletter
%\def\@copyrightspace{\relax}
%\makeatother

\begin{document}

    \newcommand{\mike}[1]{\textcolor{green}{\emph {Mike: #1}}}
    \newcommand{\mats}[1]{\textcolor{blue}{\sc Mats: #1}}
    \newcommand{\sanjai}[1]{\textcolor{magenta}{\sc Sanjai: #1}}
    \newcommand{\anitha}[1]{\textcolor{red}{\emph {Anitha: #1}}}
    \newcommand{\req}[1]{\textcolor{blue}{\begin{quotation}\emph{#1}\end{quotation}}} %\begin{quotation}
    \newcommand{\eq}[1]{\textcolor{blue}{\begin{equation} #1\end{equation}}}
    \sloppypar


\title{Revisiting the Fundamentals of Traceability between Requirements and its Realization}

\author{Anitha Murugesan, Michael Whalen, Elaheh Ghassabani and Mats Heimdahl \\
      {Department of Computer Science and Engineering}\\
      {University of Minnesota, 200 Union Street, Minneapolis, Minnesota 55455}\\
      {\{anitha, whalen, ghass013,heimdahl\}@cs.umn.edu}
}

    \maketitle

    \begin{abstract}
When establishing associations, known as \emph{ trace links}, between a requirement
and the artifacts that lead to its satisfaction, it is essential to know what the links mean.  
While research into this type of
traceability, that we call \emph{Requirements Satisfaction Traceability},
 has been an active research area for some time, none of the
literature that we have found discusses the fact that there are often multiple possible 
satisfaction arguments that each use a different set of implementation elements.
The distinction between establishing a single satisfaction argument 
between a requirement and its implementation (tracing *one* way the requirement is implemented) vs. all satisfaction arguments, and the possible ramifications for how the trace
links can be used in analysis, has not been well studied.  We examine how this distinction 
changes the way traceability is perceived, established, maintained, and used.  We introduce
and discuss the notion of ``complete" traceability, which considers *all* trace
links between the requirements and the artifacts that work to satisfy the
requirements, and contrast it with the partial traceability common in
practice.  The intent of this RE@Next! paper is to highlight the aspect of
completeness in traceability and discuss the ramifications of incomplete (or
partial) traceability.
%    \input{abstract}
    \end{abstract}

    \input{introduction}
    \input{traceability}
    \input{discussion}
    \input{setofsupport}
%    \input{background}
%    \input{related}
    \input{conclusion}

%    \input{hrrmodel}
%    \input{caseexample}

%\input{quarantine}

\bibliographystyle{abbrv}
\bibliography{crisys}

\end{document}
